Pillar 1 - Sequential Pattern Mining

### 2019-02-01 Pillar 1 - Sequential Pattern Mining.Rmd
AR_not_taken

# Probability of taken a course
d_support_take <- d_transactions %>%
  distinct(
    item,
    sequenceID
    ) %>%
  group_by(
    item
    ) %>%
  summarise(
    count     = n(),
    rate.take = count / n_students
    )

@@

    # include lhs.support
    mutate(
      lhs_course = str_remove_all(lhs, pattern = "_fail|_low")
      ) %>%
    left_join(
      select(data_support, item, !!enquo(type_rule)),
      by = c("lhs_course" = "item")
      ) %>%
    mutate(
      lhs.support = round(!!type_rule_enquo, 5)
      )  %>%
    select(
      - !!type_rule_enquo
      ) %>%

    # include rhs.support
    mutate(
      rhs_course = str_remove_all(rhs, pattern = "_fail|_low")
      ) %>%
    left_join(
      select(data_support, item, !!type_rule_enquo),
      by = c("rhs_course" = "item")
      ) %>%
    mutate(
      rhs.support = round(!!type_rule_enquo, 5)
      ) %>%
    select(
      - !!type_rule_enquo
      ) %>%

    # order variable
    select(
      lhs, rhs, support, count, confidence, rhs.support, lift, lhs.support
    )

@@

      # impose lhs and rhs to be fail
      both = d_transactions %>%
        filter(HL == "low") %>%
        distinct(`item_HL`) %>%
        pull
    ),

@@

@@

# AR_not_taken <- my_apriori(transactions_Taken)

>>>>

# Probability of taken a course
d_support_take <- d_transactions %>%
  distinct(
    item,
    sequenceID
    ) %>%
  group_by(
    item
    ) %>%
  summarise(
    count     = n(),
    rate.take = count / n_students,
    rate.not  = 1 - rate.take
    )

@@

    # include lhs.support
    mutate(
      lhs_course = str_remove_all(lhs, pattern = "_fail|_low|_not taken")
      ) %>%
    left_join(
      select(data_support, item, !!enquo(type_rule)),
      by = c("lhs_course" = "item")
      ) %>%
    mutate(
      lhs.support = round(!!type_rule_enquo, 5)
      )  %>%
    select(
      - !!type_rule_enquo
      ) %>%

    # include rhs.support
    mutate(
      rhs_course = str_remove_all(rhs, pattern = "_fail|_low|_not taken")
      ) %>%
    left_join(
      select(data_support, item, !!type_rule_enquo),
      by = c("rhs_course" = "item")
      ) %>%
    mutate(
      rhs.support = round(!!type_rule_enquo, 5)
      ) %>%
    select(
      - !!type_rule_enquo
      ) %>%

    # order variable
    select(
      lhs_course, lhs, rhs, support, count, confidence, rhs.support, lift, lhs.support
    )

@@

      # impose lhs and rhs to be low
      both = d_transactions %>%
        filter(HL == "low") %>%
        distinct(`item_HL`) %>%
        pull
    ),

@@

#
# AR not taken
AR_not_taken <- transactions_Taken %>%
  make_AR(
    appearance = list(

      # impose lhs and rhs to be not taken
      both = d_transactions_not_taken %>%
        filter(taken == "not taken") %>%
        distinct(`item_taken`) %>%
        pull
    ),

    data_support = d_support_take,
    type_rule = rate.not
  )

@@
